Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum

### 2015-12-06 DishReflectometry/Paper1_v0.tex
Almost all changes are done. New figures need to be made and inserted. Have to take careful look on the paper format.

and the measured visibility spectrum would be, 
\begin{equation}\label{eqn:series1}
\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
\end{equation}
Taking the Fourier transform of the visibility we obtain the delay spectrum
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
  			      & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
\end{eqnarray}

@@

\begin{eqnarray}\label{eqn:ratio1}
{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
\end{eqnarray}

@@

  \begin{eqnarray}\label{eqn:ratio2}
 {I_{ret} \over I_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
\end{eqnarray}

@@

Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of $50$ to
$500MHz$. This measurement was taken with the feed suspended at $4.26m$, which
was our closest measurement to the actual focal height.  Because the return
loss is the ratio of the power received to the power transmitted, higher
reflections can clearly be seen outside of the PAPER bandwidth. This is not
surprising, since the feed is tuned specifically for PAPER. The return loss
minima are locations where our feed is well-matched to free space.

In Figure \ref{fig:3bands}, the return loss we measure is plotted versus delay
for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a
typical power spectra bandwidth when using a Hamming window function. Two
additional measurements, using data taken in 2014 with the first prototype HERA
dish near Berkeley, CA, are also plotted using two different bandwidths. One of
the main differences between the Green Bank and Berkeley measurements is that
the feed was not encompassed in a cage for the Berkeley data (only a backplane). Additionally, the $50-1000MHz$ data taken in Berkeley was
Fourier-transformed internally by the measuring device, while the $100-200MHz$
data is analyzed post-measurement in the same way as the Green Bank data.

From the plot, we see that the delay response of a feed is dependent on the band chosen for the Fourier transform.  As one might expect, in regions
where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth.  Fourier transforms taken over wider bands
become dominated by the feed performance in regions outside the operating band, making the resultant delay profiles less relevant
for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
Although this may appear to be a relevant performance metric
for PAPER-style power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid
sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.

In the $100-200MHz$ delay profile, we see a delay response of $-50dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  Because
this does not achieve $-60dB$ attenuation at $60ns$, this indicates that the HERA system under test does not meet specification. However, we can learn additional information by evaluating
different feed components.

%\begin{figure}[ht!]
%\centering
%\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
%\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights. Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
%\label{fig:elevator}
%\end{figure}

Figure \ref{fig:elevator} is again a delay plot of the return loss, but for
four different feed suspension heights. We use the PAPER bandwidth and note
that the measurements are near identical at low delays, implying that low delay
reflections are caused primarily by reflections within the feed cage. However,
at higher delays we notice discrepancies between the different heights.

In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed
away from the dish. Echosorb is placed under the feed for some of the
measurements, with the expectation that it will prevent any reflections off the
ground. Measurements are also taken of the feed inside its metal cage in
various configurations. It is shown that the feed performs best without the cage and with the absorber.

From these various measurements, we find that the feed itself is responsible for a significant portion of the structure up to $60ns$ and
that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. We note that this depends strongly
on its coupling to structures around it. Structure beyond $60ns$ appears to scale
with the height of the feed above the dish, making reflections off the dish the likely culprit.

@@

The delay-domain performance of the HERA dish is central to HERA's function as a power spectrum instrument.
As we have seen, reflectometry measurements can help characterize HERA's performance in this domain, and
as Equation \ref{eqn:ratio1} shows, these measurements must be adjusted for a difference in transmission/reflection
at the first feed encounter in order to be interpreted as the delay response of a feed relative to an incident
plane wave from the sky.  We also see that the choice of windowing function is critical for accurately measuring the
antenna delay response at higher delays, where sidelobes from much higher amplitude responses at small delays can easily
dominate.  We find Hamming, Hanning, and Blackman-Harris windows to be generally adequate while square windowing functions are not.
Given the critical nature of the windowing function, we recommend that all reflectometry measurements be performed in the
frequency domain, so that the data analyst can manually implement the Fourier transform with the appropriate window.

>>>>

and the measured visibility spectrum would be, 
\begin{equation}\label{eqn:series1}
\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
\end{equation}
Taking the Fourier transform of the visibility we obtain the delay spectrum
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
  			      & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
\label{eq7}
\end{eqnarray}

@@

\begin{eqnarray}\label{eqn:ratio1}
{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
   \label{eq8}
\end{eqnarray}

@@

  \begin{eqnarray}\label{eqn:ratio2}
 {I_{ret} \over I_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
 \label{eq9}
\end{eqnarray}

@@

Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of $50$ to
$500MHz$, measured when the feed is suspended at the focal plane of the parabolic dish which is at $4.26m$ from the dish vertex. 
This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
%In Figure \ref{fig:3bands}, the return loss we measure is plotted versus delay
%for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a
%typical power spectra bandwidth when using a Hamming window function. Two
%additional measurements, using data taken in 2014 with the first prototype HERA
%dish near Berkeley, CA, are also plotted using two different bandwidths. One of
%the main differences between the Green Bank and Berkeley measurements is that
%the feed was not encompassed in a cage for the Berkeley data (only a backplane). Additionally, the $50-1000MHz$ data taken in Berkeley was
%Fourier-transformed internally by the measuring device, while the $100-200MHz$
%data is analyzed post-measurement in the same way as the Green Bank data.

The delay response of the instrument is dependent on the band chosen for the Fourier transform.
%As one might expect, in regions where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
%using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth. 
The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band. \textbf{In the $100-200MHz$ delay profile, we see a delay response of $-25dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  WRITE AGAIN}
\begin{figure}[ht!]
\centering
\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights. Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
\label{fig:elevator}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
\caption{Delay plots produced using a Hamming window function for different feed only configurations and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

Figure \ref{fig:elevator} is again a delay plot of the return loss at four different feed suspension heights. 
We use the PAPER bandwidth and note
that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. 
However, at higher delays we notice discrepancies between the different heights.
In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed only.away from the dish. Echosorb is placed under the feed for some of the
measurements, with the expectation that it will prevent any reflections off the
ground.
 Measurements are also taken of the feed inside its metal cage in various configurations. It is shown that the feed performs best without the cage and with the absorber. 
All these measurements are suggestive of the  fact that the feed-cage assembly itself is responsible for a significant portion of the structure up to $60ns$ and
that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. 
We note that this depends stronglyon its coupling to structures around it. 
Structure beyond $60ns$ appears to scale with the height of the feed above the dish.

@@

The delay-domain performance of the HERA dish is central to HERA's function as a power spectrum instrument.
As we have seen, reflectometry measurements can help characterize HERA's performance in this domain, and
as Equation \ref{eqn:ratio1} shows, these measurements must be adjusted for a difference in transmission/reflection
at the first feed encounter in order to be interpreted as the delay response of a feed relative to an incident
plane wave from the sky.  We also see that the choice of windowing function is critical for accurately measuring the
antenna delay response at higher delays, where sidelobes from much higher amplitude responses at small delays can easily
dominate.  We find Hamming, Hanning, and Blackman-Harris windows to be generally adequate while square windowing functions are not.
Given the critical nature of the windowing function, we recommend that all reflectometry measurements be performed in the
frequency domain, so that the data could be Fourier transformed with the appropriate window.
